---
title: "Instructon"
author: "Consulting Group"
date: '2022-05-03'
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE)
library(arsenal)
library(data.table)
library(tidyselect)
library(tidyverse)
library(stringr)
library(BSDA)
```

# Import the target dara
```{r}
# Get the data
df<-read.csv("consulting project.csv",header=TRUE)
```

# Get the target diagnosis code and target procedure code
```{r}
diagnosistar<-c('S02.85', 'S02.3', 'S02.12', 'S02.84', 'S02.83','802.6','802.7') 

proceduretar<-c('"16.0"', "16.01", '16.09', '16.8', '16.81', '16.89','0N5P', '0N5Q',        
                '0N8P', '0N8Q', '0N9P', '0N9Q', '0NBP', '0NBQ', '0NCP', '0NCQ', '0NDP', 
                '0NDQ', '0NHP', '0NHQ', '0NNP', '0NNQ', '0NQP', '0NQN', '0NRP', '0NRQ',
                '0NSP', '0NSQ', '0NTP', '0NTQ', '0NUP', '0NUQ')
```

# Create the function
```{r}
## Function for finding data with specific target code
get_candi<-function(target,df){                     
  tmp=startsWith(c(as.matrix(df)),target) # Use StartsWith function to detect all the observation with target code
  tmp2=data.frame(matrix(tmp,ncol=369))  # Transfer the result from previous step to data.frame
  tmp_index=apply(tmp2,1,sum,na.rm = T)>0 # Find which observation content target code and set them to TRUE index
  re=df[tmp_index,] # Get all patient with TRUE index
  return(re) # Return the result
}
```


# Get the number of patient with specific condition
## Get the total number of patient
```{r}
Num_of_patient<-nrow(df)
Num_of_patient
```

## Get the number for patient with target diagnosis code
```{r}
l<-lapply(diagnosistar,get_candi,df=df)
Onlywithdiagnosis<-distinct(bind_rows(l)) 
Num_of_patients_with_diagnosis<-nrow(Onlywithdiagnosis)
Num_of_patients_with_diagnosis
```

## Get the number for patient with both target diagnosis code and procedure code
```{r}
w<-lapply(proceduretar,get_candi,df=Onlywithdiagnosis)
Bothdiagnosis_and_procedure <-distinct(bind_rows(w)) 
Num_of_patients_with_diagnosis_and_procedure<-nrow(Bothdiagnosis_and_procedure)
Num_of_patients_with_diagnosis_and_procedure
```

## Get the number of patient with target procedure code
```{r}
v<-lapply(proceduretar,get_candi,df=df)
Onlywithprocedure<-distinct(bind_rows(v)) 
Num_of_patients_with_procedure<-nrow(Onlywithprocedure)
Num_of_patients_with_procedure
```

## Get the number of patient with target procedure code but no target diagnosis code
```{r}
Num_of_patient_with_procedure_no_daignosis<-Num_of_patients_with_procedure-Num_of_patients_with_diagnosis_and_procedure
Num_of_patient_with_procedure_no_daignosis
```

## Get the number of patient with target diagnosis but not target procedure
```{r}
Num_of_patient_with_diagnosis_no_procedure<-Num_of_patients_with_diagnosis-Num_of_patients_with_diagnosis_and_procedure
Num_of_patient_with_diagnosis_no_procedure
```

## Get the number of patient with no target diagnosis
```{r}
Num_of_patient_with_no_target_diagnosis<-Num_of_patient-Num_of_patients_with_diagnosis
Num_of_patient_with_no_target_diagnosis
```

## Get the number of patient with no target diagnosis and no target procedure
```{r}
Num_of_patient_with_no_target_diagnosis_no_procedure<-Num_of_patient_with_no_target_diagnosis-Num_of_patient_with_procedure_no_daignosis
Num_of_patient_with_no_target_diagnosis_no_procedure
```

## Get the number of patient with no target procedure
```{r}
Num_of_patient_with_no_procedure<-Num_of_patient-Num_of_patients_with_procedure
Num_of_patient_with_no_procedure
```

# Create contingency table 
```{r}
data.frame('With target procedure' = c(2,5,7),
           'With no target procedure' = c(53,258,311),
           'total '=c(55,263,318),row.names = c('With target diagnosis',
                                                'With no target diagnosis','total'))
```

# Conditional Probability
```{r}
prob<-2/55
prob
```

# Z-test part
We want to test if the population proportion (true proportion of orbital fracture patients who need surgery) is greater than a threshold 5%.
For here$\beta_{0} = 0.05$ and $\beta_{1} > 0.05$
```{r}
ztest<-prop.test(2, 55, p = 0.05, alternative = "greater", conf.level = 0.95, correct = TRUE)
ztest$p.value
```
Because 0.56146 > 0.05, so we can say this test is not significant, so cannot reject the null hypothesis.
